NumPy---Array Computation for Python

### 2020-01-09 body.tex
Add draft diagram sketches

@@

\begin{figure}
  \centering
  \includegraphics[width=0.5\linewidth]{static/broadcasting}
  \caption{\fixme{PLACEHOLDER: Stefan is working on some new figures to illustrate arrays, broadcasting, etc.}
   }
  \label{fig:broadcasting}
\end{figure}

@@

@@

>>>>

\begin{figure*}
  \centering
  \includegraphics[width=\textwidth]{static/sketches/array concepts}
  \caption{\fixme{PLACEHOLDER: This figure needs some text to describe
  it}
   }
  \label{fig:arrayconcepts}
\end{figure*}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{static/sketches/fancy indexing}
  \caption{\fixme{Indexing using arrays, or ``fancy indexing''.}
   }
  \label{fig:broadcasting}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{static/sketches/reductions}
  \caption{\fixme{Reducing an array along one of several axes.}
   }
  \label{fig:reductions}
\end{figure}

@@

\begin{figure*}
  \centering
  \includegraphics[width=0.8\textwidth]{static/sketches/duck arrays}
  \caption{\fixme{Examples of so-called ``duck arrays'': arrays
  implemented by another library that behave like NumPy arrays, and
  support NumPy operations.  Through protocols, it is possible to have
  a call such as $\cos(\cdot)$ succeed on each of these.}}
  \label{fig:arrayconcepts}
\end{figure*}
